Tampering Detection In Low-Power Smart Cameras

### 2015-05-28 paper.tex
minor edits

In particular, camera displacement and occlusions are typically detected by background models or frame comparison, while blurring is instead detected by monitoring the high-frequency component of images, as this is expected to drop. In ~\cite{aksay2007camera} and~\cite{saglam2009real} tampering is detected by comparing histograms of background and current frame, and by monitoring the energy in wavelet or Fourier domain. Two background models computed over different time intervals are used in~\cite{saglam2009real}. In~\cite{gil2007automatic}, tampering detection is performed by combining background subtraction together with edge detection and normalized cross-correlation. Background models and block matching in~\cite{tsesmelis2013tamper} enable the displacement detection, while number of SURF~\cite{bay2006surf} keypoints is used to detect blurring. A frame buffer rather than an explicit background is used~\cite{ribnick2006real}. All these solutions, including~\cite{ribnick2006real,harasse2004automated,kryjak2012fpga} are computationally demanding, and are not viable options for low-power cameras.

@@

Segmentation consists in clustering the feature vectors~\eqref{eq:featureVector} over the whole image by means of a weighted version of the k-means algorithm~\cite{kottke1994motion}. In particular, since the components of the feature vector span very different ranges, the distance between a feature vector and any cluster's centroid, is weighted by the standard deviation of each component for each cluster.

@@

We have acquired two datasets to test our method. The first dataset contains \gi{how many?} sequences taken from webcams recording urban areas (as in Figure \ref{fig:sequences}(a)), where we have synthetically introduced blurring by means of a gaussian filters (Figure \ref{fig:sequences}(b)), and displacement by concatenating frames from sequences depicting similar environments (Figure \ref{fig:sequences}(c)). In some cases, sequences contained real tampering events, as in Figure \ref{fig:indicatori}.\\

The second dataset was recorded using a Raspberry Pi Model B+, with its camera module, and the tampering was introduced by moving the device or spraying water on the camera lens.\gi{una footnote dicendo sequences can be released upon request?}

>>>>

In particular, camera displacement and occlusions are typically detected by background models or frame comparison, while blurring is instead detected by monitoring the high-frequency component of images, as this is expected to drop. In ~\cite{aksay2007camera} and~\cite{saglam2009real} tampering is detected by comparing histograms of background and current frame, and by monitoring the energy in wavelet or Fourier domain. Two background models computed over different time intervals are used in~\cite{saglam2009real}. In~\cite{gil2007automatic}, tampering detection is performed by combining background subtraction together with edge detection and normalized cross-correlation. Background models and block matching in~\cite{tsesmelis2013tamper} enable the displacement detection, while number of SURF~\cite{SURF} keypoints is used to detect blurring. A frame buffer rather than an explicit background is used~\cite{ribnick2006real}. All these solutions, including~\cite{ribnick2006real,harasse2004automated,kryjak2012fpga} are computationally demanding, and are not viable options for low-power cameras.

@@

Segmentation consists in clustering the feature vectors~\eqref{eq:featureVector} over the whole image by a weighted k-means~\cite{kottke1994motion}. In particular, since the components of the feature vector span very different ranges, when computing the distance between a feature vector and any cluster's centroid, we scale the distance on each component by its standard deviation.

@@

We have acquired two datasets to test our method. The first dataset contains \gi{how many?} sequences taken from webcams recording urban areas (as in Figure \ref{fig:sequences}(a)), where we have synthetically introduced blurring by means of a gaussian filters (Figure \ref{fig:sequences}(b)), and displacement by concatenating frames from sequences depicting similar environments (Figure \ref{fig:sequences}(c)). In some cases, sequences contained real tampering events, as in Figure \ref{fig:sequences}(d).\\

The second dataset was recorded using a Raspberry Pi Model B+, with its camera module, and the tampering was introduced by moving the device or spraying water on the camera len.\gi{una footnote dicendo sequences can be released upon request?}
